\begin{thebibliography}{99}
\small  % Reduce font size for all references

\bibitem[Anselin(1988)]{anselin1988spatial}
Anselin, L. (1988).
\newblock {\em Spatial Econometrics: Methods and Models}.
\newblock Kluwer Academic Publishers.

\bibitem[Bai and Perron(2003)]{bai2003computation}
Bai, J., \& Perron, P. (2003).
\newblock Computation and Analysis of Multiple Structural Change Models.
\newblock {\em Journal of Applied Econometrics}, 18(1), 1--22.

\bibitem[Barrett(2001)]{barrett2001measuring}
Barrett, C. B. (2001).
\newblock Measuring Integration and Efficiency in International Agricultural Markets.
\newblock {\em Review of Agricultural Economics}, 23(1), 19--32.

\bibitem[Baulch(1997)]{baulch1997transfer}
Baulch, B. (1997).
\newblock Transfer Costs, Spatial Arbitrage, and Testing for Food Market Integration.
\newblock {\em American Journal of Agricultural Economics}, 79(2), 477--487.

\bibitem[Breusch and Pagan(1979)]{breusch1979simple}
Breusch, T. S., \& Pagan, A. R. (1979).
\newblock A Simple Test for Heteroskedasticity and Random Coefficient Variation.
\newblock {\em Econometrica}, 47(5), 1287--1294.

\bibitem[Dercon(1995)]{dercon1995market}
Dercon, S. (1995).
\newblock On Market Integration and Liberalisation: Method and Application to Ethiopia.
\newblock {\em Journal of Development Studies}, 32(1), 112--143.

\bibitem[Dickey and Fuller(1979)]{dickey1979distribution}
Dickey, D. A., \& Fuller, W. A. (1979).
\newblock Distribution of the Estimators for Autoregressive Time Series with a Unit Root.
\newblock {\em Journal of the American Statistical Association}, 74(366a), 427--431.

\bibitem[Durbin and Watson(1950)]{durbin1950testing}
Durbin, J., \& Watson, G. S. (1950).
\newblock Testing for Serial Correlation in Least Squares Regression. I.
\newblock {\em Biometrika}, 37(3/4), 409--428.

\bibitem[Engle and Granger(1987)]{engle1987cointegration}
Engle, R. F., \& Granger, C. W. J. (1987).
\newblock Co-integration and Error Correction: Representation, Estimation, and Testing.
\newblock {\em Econometrica}, 55(2), 251--276.

\bibitem[Engle and Yoo(1987)]{engle1987forecasting}
Engle, R. F., \& Yoo, B. S. (1987).
\newblock Forecasting and Testing in Cointegrated Systems.
\newblock {\em Journal of Econometrics}, 35(1), 143--159.

\bibitem[Fackler and Goodwin(2001)]{fackler2001spatial}
Fackler, P. L., \& Goodwin, B. K. (2001).
\newblock Spatial Price Analysis.
\newblock In {\em Handbook of Agricultural Economics}, Vol. 1, 971--1024.
\newblock Elsevier.

\bibitem[Fackler and Tastan(2008)]{fackler2008estimating}
Fackler, P. L., \& Tastan, H. (2008).
\newblock Estimating the Degree of Market Integration.
\newblock {\em American Journal of Agricultural Economics}, 90(1), 69--85.

\bibitem[Hansen and Seo(2002)]{hansen2002testing}
Hansen, B. E., \& Seo, B. (2002).
\newblock Testing for Two-Regime Threshold Cointegration in Vector Error-Correction Models.
\newblock {\em Journal of Econometrics}, 110(2), 293--318.

\bibitem[Jarque and Bera(1987)]{jarque1987test}
Jarque, C. M., \& Bera, A. K. (1987).
\newblock A Test for Normality of Observations and Regression Residuals.
\newblock {\em International Statistical Review}, 55(2), 163--172.

\bibitem[Johansen(1988)]{johansen1988statistical}
Johansen, S. (1988).
\newblock Statistical Analysis of Cointegration Vectors.
\newblock {\em Journal of Economic Dynamics and Control}, 12(2-3), 231--254.

\bibitem[Johansen(1995)]{johansen1995}
Johansen, S. (1995).
\newblock {\em Likelihood-Based Inference in Cointegrated Vector Autoregressive Models}.
\newblock Oxford University Press.

\bibitem[Johansen and Juselius(1990)]{johansen1990maximum}
Johansen, S., \& Juselius, K. (1990).
\newblock Maximum Likelihood Estimation and Inference on Cointegration---with Applications to the Demand for Money.
\newblock {\em Oxford Bulletin of Economics and Statistics}, 52(2), 169--210.

\bibitem[Kwiatkowski et al.(1992)]{kwiatkowski1992testing}
Kwiatkowski, D., Phillips, P. C., Schmidt, P., \& Shin, Y. (1992).
\newblock Testing the Null Hypothesis of Stationarity Against the Alternative of a Unit Root.
\newblock {\em Journal of Econometrics}, 54(1-3), 159--178.

\bibitem[LeSage and Pace(2009)]{lesage2009}
LeSage, J., \& Pace, R. K. (2009).
\newblock {\em Introduction to Spatial Econometrics}.
\newblock CRC Press.

\bibitem[Little(2007)]{little2007unofficial}
Little, P. D. (2007).
\newblock Unofficial Cross-Border Trade in Eastern Africa.
\newblock {\em Food Policy}, 32(3), 479--492.

\bibitem[Lütkepohl(2005)]{lutkepohl2005}
Lütkepohl, H. (2005).
\newblock {\em New Introduction to Multiple Time Series Analysis}.
\newblock Springer.

\bibitem[Mansour et al.(2021)]{mansour2021market}
Mansour, A., Salam, A., \& Nabil, M. (2021).
\newblock Market Dynamics in Syria's War Economy.
\newblock {\em Journal of Development Studies}, 57(6), 985--1002.

\bibitem[McNew(1996)]{mcnew1996spatial}
McNew, K. (1996).
\newblock Spatial Market Integration: Definition, Theory, and Evidence.
\newblock {\em Agricultural and Resource Economics Review}, 25(1), 1--11.

\bibitem[Negassa and Myers(2007)]{negassa2007estimating}
Negassa, A., \& Myers, R. J. (2007).
\newblock Estimating Policy Effects on Spatial Market Efficiency: An Extension to the Parity Bounds Model.
\newblock {\em American Journal of Agricultural Economics}, 89(2), 338--352.

\bibitem[Rashid et al.(2008)]{rashid2008spatial}
Rashid, S., Gulati, A., \& Cummings Jr, R. (2008).
\newblock From Parastatals to Private Trade: Lessons from Asian Agriculture.
\newblock {\em Food Policy}, 33(4), 305--317.

\bibitem[Ravallion(1986)]{ravallion1986testing}
Ravallion, M. (1986).
\newblock Testing Market Integration.
\newblock {\em American Journal of Agricultural Economics}, 68(1), 102--109.

\bibitem[Sims(1980)]{sims1980macroeconomics}
Sims, C. A. (1980).
\newblock Macroeconomics and Reality.
\newblock {\em Econometrica}, 48(1), 1--48.

\bibitem[World Bank(2022)]{worldbank2022yemen}
World Bank. (2022).
\newblock Yemen Economic Monitoring Report.
\newblock World Bank Publications.

\end{thebibliography}
